---
title: "Entitlement Final Analysis"
output: 
  html_document:
    toc: true
---

```{r include = FALSE}
library(tidyverse)
library(lme4)
library(reshape)
library(psych)
library(Hmisc)
library(lmerTest)
library(nnet)
library(broom)
library(gridExtra)

# setwd("/Users/seantrott/Dropbox/UCSD/Research/IndirectSpeechActs/Entitlement/entitlement_data_analysis/analysis")
```



# Norm information



```{r}
df_normed = read_csv("../data/norming_data.csv")
df_normed$Age = as.integer(df_normed$Age)
df_normed$condition = factor(df_normed$stimType)
df_normed$situation = factor(df_normed$type)
```

## Experiment info

```{r}
length(unique(df_normed$subject))
table(distinct(df_normed, subject, Gender)$Gender)
mean(distinct(df_normed, subject, Age)$Age, na.rm=TRUE)
sd(distinct(df_normed, subject, Age)$Age, na.rm=TRUE)
range(distinct(df_normed, subject, Age)$Age, na.rm=TRUE)

```

## Average completion time

```{r}
df_rt = df_normed %>%
  group_by(subject) %>%
  summarise(total_minutes = sum(rt) / 60000)

mean(df_rt$total_minutes)
```



## Inter-correlations

```{r}
cor_table = df_normed %>%
  select(entitlement_norm, power_norm, imposition_norm, distance_norm) %>%
  na.omit() %>%
  as.matrix() %>%
  rcorr(type=c("pearson"))

cor_table
```


## Descriptive stats

```{r}
df_normed %>%
  group_by(stimType) %>%
  summarise(mean_entitlement = mean(entitlement_norm, na.rm=TRUE),
            sd_entitlement = sd(entitlement_norm, na.rm=TRUE),
            mean_imposition = mean(imposition_norm, na.rm=TRUE),
            sd_imposition = sd(imposition_norm, na.rm=TRUE),
            mean_power = mean(power_norm, na.rm=TRUE),
            sd_power = sd(power_norm, na.rm=TRUE),
            mean_distance = mean(distance_norm, na.rm=TRUE),
            sd_distance = sd(distance_norm, na.rm=TRUE)
            )


summary(lm(data = df_normed,
           entitlement_norm ~ stimType))
summary(lm(data = df_normed,
           imposition_norm ~ stimType))
summary(lm(data = df_normed,
           power_norm ~ stimType))
summary(lm(data = df_normed,
           distance_norm ~ stimType))


df_normed %>%
  group_by(stimNum, stimType) %>%
  summarise(mean_entitlement = mean(entitlement_norm, na.rm=TRUE),
            sd_entitlement = sd(entitlement_norm, na.rm=TRUE),
            mean_imposition = mean(imposition_norm, na.rm=TRUE),
            sd_imposition = sd(imposition_norm, na.rm=TRUE),
            mean_power = mean(power_norm, na.rm=TRUE),
            sd_power = sd(power_norm, na.rm=TRUE),
            mean_distance = mean(distance_norm, na.rm=TRUE),
            sd_distance = sd(distance_norm, na.rm=TRUE)
            )

```


```{r}

m1_entitlement = lm(data = df_normed,
          entitlement_norm ~ condition * situation + Gender)
summary(m1_entitlement)


m1_power = lm(data = df_normed,
          power_norm ~ condition * situation)
summary(m1_power)


m1_imposition = lm(data = df_normed,
          imposition_norm ~ condition * situation)
summary(m1_imposition)

m1_distance = lm(data = df_normed,
          distance_norm ~ condition * situation)
summary(m1_distance)
```


# Experiment 1

```{r}

coded_with_norms = read_csv("../data/exp1_critical.csv")
coded_with_norms$formatting = factor(coded_with_norms$formatting)

```


## Average completion time

```{r}
df_rt = coded_with_norms %>%
  group_by(subject) %>%
  summarise(total_minutes = sum(rt) / 60000)

mean(df_rt$total_minutes)
```


## Experiment info

```{r}
length(unique(coded_with_norms$subject))
table(distinct(coded_with_norms, subject, Gender)$Gender)
mean(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
sd(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
range(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)

```

## Formatting ~ Entitlement

```{r}
model_full = glmer(data = coded_with_norms,
                  formatting ~ condition + Gender +
                    (1 | subject) + (1 | stimNum),
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)


model_full = glmer(data = coded_with_norms,
                  formatting ~ condition + Gender +
                    (1 + condition | subject) + (1 + condition | stimNum),
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_reduced = glmer(data = coded_with_norms,
                  formatting ~ Gender +
                    (1 + condition | subject) + (1 + condition | stimNum),
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

anova(model_full, model_reduced)

model_gender_interaction = glmer(data = coded_with_norms,
                  formatting ~ condition * Gender +
                    (1 + condition | subject) + (1 + condition | stimNum),
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

anova(model_full, model_gender_interaction)


```


### Use multinomial regression to extract weights

```{r}
model_formatting_full = multinom(formatting ~ condition +
                              Gender,
                        data = coded_with_norms)

z <- summary(model_formatting_full)$coefficients/summary(model_formatting_full)$standard.errors
# 2-tailed Wald z tests to test significance of coefficients
p <- (1 - pnorm(abs(z), 0, 1)) * 2

summary(model_formatting_full)
p


```


### Visualization


```{r}
### Code for making stacked bar chart
s = as.data.frame(table(coded_with_norms$condition, coded_with_norms$formatting))
s = filter(s, Var1 != "filler")

low = filter(s, Var1 == "low")
low$proportion = low$Freq/sum(low$Freq)
high = filter(s, Var1 == "high")
high$proportion = high$Freq/sum(high$Freq)

new.prop = rbind(low, high)

new.prop$Var2 = factor(new.prop$Var2, levels = c("D", "M", "EM", "IS"))
new.prop$Var2 = new.prop$Var2 %>%
  fct_recode("Direct" = "D",
             "Modal" = "M",
             "Embedded Modal" = "EM",
             "Indirect Statement" = "IS")

exp1 = ggplot(data=new.prop, aes(x=Var1, y=proportion, fill=Var2, label = round(proportion, 2))) +
  geom_bar(stat="identity") +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  theme_minimal() +
  xlab("Entitlement") +
  guides(fill=guide_legend(title="Formatting")) +
  ggtitle("Formatting rates across conditions (Experiment 1)") +
  ylab("Proportion of requests") 

# ggsave("Figures/s1_exp2_stacked.tiff", units="in", width=4, height=4, dpi=300, compression = 'lzw')



```


## Formatting ~ Entitlement Norms


```{r}

model_formatting_full = glmer(formatting ~ mean_entitlement +
                              mean_power +
                              mean_imposition +
                              mean_distance +
                              Gender +
                          (1 + mean_entitlement | subject) +
                          (1 | stimNum),
                        data = coded_with_norms, 
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_formatting_no_entitlement = glmer(formatting ~  mean_power +
                                   mean_imposition +
                                   mean_distance +
                                   Gender + 
                          (1 + mean_entitlement | subject) +
                          (1 | stimNum),
                        data = coded_with_norms, 
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_formatting_no_power = glmer(formatting ~  mean_entitlement +
                                   mean_imposition +
                                   mean_distance +
                                   Gender + 
                          (1 + mean_entitlement | subject) +
                          (1 | stimNum),
                        data = coded_with_norms, 
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_formatting_no_imposition = glmer(formatting ~  mean_power +
                                   mean_entitlement +
                                   mean_distance +
                                   Gender + 
                          (1 + mean_entitlement | subject) +
                          (1 | stimNum),
                        data = coded_with_norms, 
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_formatting_no_distance = glmer(formatting ~  mean_power +
                                   mean_imposition +
                                   mean_entitlement +
                                   Gender + 
                          (1 + mean_entitlement | subject) +
                          (1 | stimNum),
                        data = coded_with_norms, 
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

anova(model_formatting_full, model_formatting_no_entitlement)
anova(model_formatting_full, model_formatting_no_power)
anova(model_formatting_full, model_formatting_no_imposition)
anova(model_formatting_full, model_formatting_no_distance)
```

### Adjust for multiple comparisons

```{r}
p1 = anova(model_formatting_full, model_formatting_no_entitlement)$`Pr(>Chisq)`[2]
p2 = anova(model_formatting_full, model_formatting_no_power)$`Pr(>Chisq)`[2]
p3 = anova(model_formatting_full, model_formatting_no_imposition)$`Pr(>Chisq)`[2]
p4 = anova(model_formatting_full, model_formatting_no_distance)$`Pr(>Chisq)`[2]

p.adjust(c(p1, p2, p3, p4), method="holm")
```

```{r}
summary(model_formatting_full)
```

### Use multinomial regression to extract weights

```{r}
model_formatting_full = multinom(formatting ~ mean_entitlement +
                              mean_power +
                              mean_imposition +
                              mean_distance +
                              Gender,
                        data = coded_with_norms)

z <- summary(model_formatting_full)$coefficients/summary(model_formatting_full)$standard.errors
# 2-tailed Wald z tests to test significance of coefficients
p <- (1 - pnorm(abs(z), 0, 1)) * 2

summary(model_formatting_full)
p


```



# Experiment 1b

```{r}
coded_with_norms = read.csv("../data/exp1b_critical.csv")

coded_with_norms$formatting = fct_recode(coded_with_norms$formatting,
                                         "EM" = "W")
```


## Average completion time

```{r}
df_rt = coded_with_norms %>%
  group_by(subject) %>%
  summarise(total_minutes = sum(rt) / 60000)

mean(df_rt$total_minutes)
```


## Experiment info

```{r}
length(unique(coded_with_norms$subject))
table(distinct(coded_with_norms, subject, Gender)$Gender)
mean(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
sd(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
range(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
```

## Formatting ~ Entitlement

```{r}
model_full = glmer(data = coded_with_norms,
                  formatting ~ condition + Gender +
                    (1 + condition | subject) + (1 + condition | stimNum),
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_reduced = glmer(data = coded_with_norms,
                  formatting ~ Gender+
                    (1 + condition | subject) + (1 + condition | stimNum),
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

anova(model_full, model_reduced)

model_gender_interaction = glmer(data = coded_with_norms,
                  formatting ~ condition * Gender +
                    (1 + condition | subject) + (1 + condition | stimNum),
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

anova(model_gender_interaction, model_full)


```



### Use multinomial regression to extract weights

```{r}
model_formatting_full = multinom(formatting ~ condition +
                              Gender,
                        data = coded_with_norms)

z <- summary(model_formatting_full)$coefficients/summary(model_formatting_full)$standard.errors
# 2-tailed Wald z tests to test significance of coefficients
p <- (1 - pnorm(abs(z), 0, 1)) * 2

summary(model_formatting_full)
p


```




### Visualization


```{r}
### Code for making stacked bar chart
s = as.data.frame(table(coded_with_norms$condition, coded_with_norms$formatting))
s = filter(s, Var1 != "filler")

low = filter(s, Var1 == "low")
low$proportion = low$Freq/sum(low$Freq)
high = filter(s, Var1 == "high")
high$proportion = high$Freq/sum(high$Freq)

new.prop = rbind(low, high)

new.prop$Var2 = factor(new.prop$Var2, levels = c("D", "M", "EM", "IS"))
new.prop$Var2 = new.prop$Var2 %>%
  fct_recode("Direct" = "D",
             "Modal" = "M",
             "Embedded Modal" = "EM",
             "Indirect Statement" = "IS")

exp1b = ggplot(data=new.prop, aes(x=Var1, y=proportion, fill=Var2, label = round(proportion, 2))) +
  geom_bar(stat="identity") +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  theme_minimal() +
  xlab("Entitlement") +
  guides(fill=guide_legend(title="Formatting")) +
  ggtitle("Formatting rates across conditions (Experiment 1b)") +
  ylab("Proportion of requests") 

g <- arrangeGrob(exp1, exp1b, ncol=1) #generates g
ggsave(g, file="Figures/s1_both_1_1b.tiff", units="in",dpi=300, compression = 'lzw')
 



```




## Formatting ~ Entitlement Norms

```{r}
model_formatting_full = glmer(formatting ~ mean_entitlement +
                                   mean_power +
                                   mean_imposition +
                                   mean_distance +
                                   Gender + 
                          (1 + mean_entitlement | subject) +
                          (1 | stimNum),
                        data = coded_with_norms, 
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_formatting_no_entitlement = glmer(formatting ~  mean_power +
                                   mean_imposition +
                                   mean_distance +
                                   Gender + 
                          (1 + mean_entitlement | subject) +
                          (1 | stimNum),
                        data = coded_with_norms, 
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_formatting_no_power = glmer(formatting ~  mean_entitlement +
                                   mean_imposition +
                                   mean_distance +
                                   Gender + 
                          (1 + mean_entitlement | subject) +
                          (1 | stimNum),
                        data = coded_with_norms, 
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_formatting_no_imposition = glmer(formatting ~  mean_power +
                                   mean_entitlement +
                                   mean_distance +
                                   Gender + 
                          (1 + mean_entitlement | subject) +
                          (1 | stimNum),
                        data = coded_with_norms, 
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_formatting_no_distance = glmer(formatting ~  mean_power +
                                   mean_imposition +
                                   mean_entitlement +
                                   Gender + 
                          (1 + mean_entitlement | subject) +
                          (1 | stimNum),
                        data = coded_with_norms, 
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

anova(model_formatting_full, model_formatting_no_entitlement)
anova(model_formatting_full, model_formatting_no_power)
anova(model_formatting_full, model_formatting_no_imposition)
anova(model_formatting_full, model_formatting_no_distance)
```

### Adjust for multiple comparisons

```{r}
p1 = anova(model_formatting_full, model_formatting_no_entitlement)$`Pr(>Chisq)`[2]
p2 = anova(model_formatting_full, model_formatting_no_power)$`Pr(>Chisq)`[2]
p3 = anova(model_formatting_full, model_formatting_no_imposition)$`Pr(>Chisq)`[2]
p4 = anova(model_formatting_full, model_formatting_no_distance)$`Pr(>Chisq)`[2]

p.adjust(c(p1, p2, p3, p4), method="holm")
```

### Use multinomial regression to extract weights

```{r}
model_formatting_full = multinom(formatting ~ mean_entitlement +
                              mean_power +
                              mean_imposition +
                              mean_distance +
                              Gender,
                        data = coded_with_norms)

z <- summary(model_formatting_full)$coefficients/summary(model_formatting_full)$standard.errors
# 2-tailed Wald z tests to test significance of coefficients
p <- (1 - pnorm(abs(z), 0, 1)) * 2

summary(model_formatting_full)
p


```

# Experiment 2

```{r}
coded_with_norms = read.csv("../data/exp2_critical.csv")
```


## Average completion time

```{r}
df_rt = coded_with_norms %>%
  group_by(subject) %>%
  summarise(total_minutes = sum(rt) / 60000)

mean(df_rt$total_minutes)
```


## Experiment info

```{r}
length(unique(coded_with_norms$subject))
table(distinct(coded_with_norms, subject, Gender)$Gender)
mean(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
sd(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
range(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
```



## Formatting ~ Entitlement

```{r}
model_full = glmer(data = coded_with_norms,
                  formatting ~ condition + Gender+
                    (1 + condition | subject) + (1 + condition | stimNum),
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

model_reduced = glmer(data = coded_with_norms,
                  formatting ~ Gender+
                    (1 + condition | subject) + (1 + condition | stimNum),
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

anova(model_full, model_reduced)

model_gender_interaction = glmer(data = coded_with_norms,
                  formatting ~ condition * Gender+
                    (1 + condition | subject) + (1 + condition | stimNum),
                        control=glmerControl(optimizer="bobyqa"),
                        family=binomial)

anova(model_gender_interaction, model_full)



```

### Use multinomial regression to extract weights

```{r}
model_formatting_full = multinom(formatting ~ condition +
                              Gender,
                        data = coded_with_norms)

z <- summary(model_formatting_full)$coefficients/summary(model_formatting_full)$standard.errors
# 2-tailed Wald z tests to test significance of coefficients
p <- (1 - pnorm(abs(z), 0, 1)) * 2

summary(model_formatting_full)
p


```


### Visualization


```{r}
### Code for making stacked bar chart
s = as.data.frame(table(coded_with_norms$condition, coded_with_norms$formatting))
s = filter(s, Var1 != "filler")

low = filter(s, Var1 == "low")
low$proportion = low$Freq/sum(low$Freq)
high = filter(s, Var1 == "high")
high$proportion = high$Freq/sum(high$Freq)

new.prop = rbind(low, high)

new.prop$Var2 = factor(new.prop$Var2, levels = c("D", "M", "EM", "IS"))
new.prop$Var2 = new.prop$Var2 %>%
  fct_recode("Direct" = "D",
             "Modal" = "M",
             "Embedded Modal" = "EM",
             "Indirect Statement" = "IS")

ggplot(data=new.prop, aes(x=Var1, y=proportion, fill=Var2, label = round(proportion, 2))) +
  geom_bar(stat="identity", position="dodge") +
  geom_text(aes(label=round(proportion, 2)), 
            position=position_dodge(width=0.9),
            vjust=-0.25, size = 3) +
  theme_minimal() +
  xlab("Entitlement") +
  guides(fill=guide_legend(title="Formatting")) +
  ggtitle("Formatting rates across conditions") +
  ylab("Proportion of requests")

ggsave("Figures/fig1_exp2.tiff", units="in", width=5, height=4, dpi=300, compression = 'lzw')

ggplot(data=new.prop, aes(x=Var1, y=proportion, fill=Var2, label = round(proportion, 2))) +
  geom_bar(stat="identity") +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) +
  theme_minimal() +
  xlab("Entitlement") +
  guides(fill=guide_legend(title="Formatting")) +
  ggtitle("Formatting rates across conditions") +
  ylab("Proportion of requests") 

ggsave("Figures/s1_exp2_stacked.tiff", units="in", width=4, height=4, dpi=300, compression = 'lzw')



```



## Formatting ~ Entitlement Norms

```{r}
model_full_all_norms = glmer(formatting ~ mean_entitlement + 
                              mean_power + mean_imposition + mean_distance + 
                              Gender +
                              (1 + mean_entitlement | subject) +
                              (1 + mean_entitlement | stimNum), 
                            data = coded_with_norms, 
                            control=glmerControl(optimizer="bobyqa"),
                            family=binomial)

model_full_no_entitlement = glmer(formatting ~ mean_power + mean_imposition + mean_distance + 
                              Gender + (1 + mean_entitlement | subject) +
                              (1 + mean_entitlement | stimNum), 
                            data = coded_with_norms, 
                            control=glmerControl(optimizer="bobyqa"),
                            family=binomial)

model_full_no_power = glmer(formatting ~ mean_entitlement + mean_imposition + mean_distance + 
                              Gender + (1 + mean_entitlement | subject) +
                              (1 + mean_entitlement | stimNum), 
                            data = coded_with_norms, 
                            control=glmerControl(optimizer="bobyqa"),
                            family=binomial)

model_full_no_imposition = glmer(formatting ~ mean_power + mean_entitlement + mean_distance + 
                              Gender + (1 + mean_entitlement | subject) +
                              (1 + mean_entitlement | stimNum), 
                            data = coded_with_norms, 
                            control=glmerControl(optimizer="bobyqa"),
                            family=binomial)

model_full_no_distance = glmer(formatting ~ mean_power + mean_imposition + mean_entitlement + 
                              Gender + (1 + mean_entitlement | subject) +
                              (1 + mean_entitlement | stimNum), 
                            data = coded_with_norms, 
                            control=glmerControl(optimizer="bobyqa"),
                            family=binomial)

anova(model_full_all_norms, model_full_no_entitlement)
anova(model_full_all_norms, model_full_no_power)
anova(model_full_all_norms, model_full_no_imposition)
anova(model_full_all_norms, model_full_no_distance)
```

### Adjust for multiple comparisons

```{r}
p1 = anova(model_full_all_norms, model_full_no_entitlement)$`Pr(>Chisq)`[2]
p2 = anova(model_full_all_norms, model_full_no_power)$`Pr(>Chisq)`[2]
p3 = anova(model_full_all_norms, model_full_no_imposition)$`Pr(>Chisq)`[2]
p4 = anova(model_full_all_norms, model_full_no_distance)$`Pr(>Chisq)`[2]

p.adjust(c(p1, p2, p3, p4), method="holm")
```


### Use multinomial regression to extract weights

```{r}
model_formatting_full = multinom(formatting ~ condition +
                                   Gender,
                        data = coded_with_norms)

z <- summary(model_formatting_full)$coefficients/summary(model_formatting_full)$standard.errors
# 2-tailed Wald z tests to test significance of coefficients
p <- (1 - pnorm(abs(z), 0, 1)) * 2

summary(model_formatting_full)
p

model_formatting_full = multinom(formatting ~ mean_entitlement +
                              mean_power +
                              mean_imposition +
                              mean_distance +
                              Gender,
                        data = coded_with_norms)

z <- summary(model_formatting_full)$coefficients/summary(model_formatting_full)$standard.errors
# 2-tailed Wald z tests to test significance of coefficients
p <- (1 - pnorm(abs(z), 0, 1)) * 2

summary(model_formatting_full)
p
```



# Experiment 3

```{r}
coded_with_norms = read.csv("../data/exp3_critical.csv")

```

## Average completion time

```{r}
df_rt = coded_with_norms %>%
  group_by(subject) %>%
  summarise(total_minutes = sum(rt) / 60000)

mean(df_rt$total_minutes)
```


## Experiment info

```{r}
length(unique(coded_with_norms$subject))
table(distinct(coded_with_norms, subject, Gender)$Gender)
mean(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
sd(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
range(distinct(coded_with_norms, subject, Age)$Age, na.rm=TRUE)
```

## Appropriateness ~ Entitlement and Formatting

Here, we predict appropriateness judgments from formatting and entitlement. Because the **wonder** (e.g. "Embedded Modal") condition doesn't really change as a function of entitlement, we make the coefficients more interpretable by selecting Embedded Modal as our reference intercept.


```{r}
t.test(filter(coded_with_norms, formatting == "wonder" & condition == "high")$judgment,
       filter(coded_with_norms, formatting == "wonder" & condition == "low")$judgment)

t.test(filter(coded_with_norms, formatting == "modal" & condition == "high")$judgment,
       filter(coded_with_norms, formatting == "modal" & condition == "low")$judgment)

t.test(filter(coded_with_norms, formatting == "direct" & condition == "high")$judgment,
       filter(coded_with_norms, formatting == "direct" & condition == "low")$judgment)

t.test(filter(coded_with_norms, formatting == "indirect" & condition == "high")$judgment,
       filter(coded_with_norms, formatting == "indirect" & condition == "low")$judgment)
```


```{r}

coded_with_norms$format_reordered = factor(coded_with_norms$formatting,
                                           levels =c("wonder",
                                                     "direct",
                                                     "indirect",
                                                     "modal"))

coded_with_norms$entitlement_reordered = factor(coded_with_norms$condition,
                                           levels =c("low", "high"))


model_full_all = lmer(judgment ~ format_reordered*entitlement_reordered + 
                              Gender +
                             (1+condition| subject) + 
                              (1 + condition | stimNum) +
                             (1 + condition | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

model_no_interaction = lmer(judgment ~ formatting + entitlement_reordered + 
                              Gender +
                             (1+condition| subject) + 
                              (1 + condition | stimNum) +
                             (1 + condition | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

model_no_formatting = lmer(judgment ~ entitlement_reordered + 
                              Gender +
                             (1+condition| subject) + 
                              (1 + condition | stimNum) +
                             (1 + condition | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

model_no_entitlement = lmer(judgment ~ formatting + 
                              Gender +
                             (1+condition| subject) + 
                              (1 + condition | stimNum) +
                             (1 + condition | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

summary(model_full_all)
anova(model_full_all, model_no_interaction)
anova(model_no_interaction, model_no_formatting)
anova(model_no_interaction, model_no_entitlement)



model_gender_two_way= lmer(judgment ~ format_reordered*entitlement_reordered + 
                             Gender*format_reordered +
                             Gender*entitlement_reordered+
                             (1+condition| subject) + 
                              (1 + condition | stimNum) +
                             (1 + condition | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

model_gender_interaction = lmer(judgment ~ format_reordered*entitlement_reordered * Gender + 
                             (1+condition| subject) + 
                              (1 + condition | stimNum) +
                             (1 + condition | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

anova(model_gender_interaction, model_gender_two_way)

```




### Model comparisons for effect of entitlement

Below, we see that an interaction between *normed entitlement* and *formatting* explains more variance than a model including norms for all other interpersonal variables (and their interactions with formatting). In other words, *perceived entitlement* explains additional variance in how appropriate different formatting options are judged to be.

```{r}


model_full_all_norms = lmer(judgment ~ format_reordered*mean_entitlement + 
                              format_reordered*mean_power +
                              format_reordered*mean_distance +
                              format_reordered*mean_imposition +
                              Gender +
                             (1+mean_entitlement| subject) + 
                              (1 + mean_entitlement | stimNum) +
                             (1 | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

model_no_entitlement_interaction = lmer(judgment ~ mean_entitlement + 
                              format_reordered*mean_power +
                              format_reordered*mean_distance +
                              format_reordered*mean_imposition +
                              Gender +
                             (1+mean_entitlement| subject) + 
                                (1 + mean_entitlement | stimNum) +
                             (1 | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

model_no_entitlement = lmer(judgment ~ format_reordered*mean_power +
                              format_reordered*mean_distance +
                              format_reordered*mean_imposition +
                              Gender +
                             (1+mean_entitlement| subject) + 
                               (1 + mean_entitlement | stimNum) +
                             (1 | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

anova(model_full_all_norms, model_no_entitlement_interaction)
anova(model_no_entitlement_interaction, model_no_entitlement)

```


### Visualizations

```{r}
coded_with_norms$formatting = fct_recode(factor(coded_with_norms$formatting), "embedded modal" = "wonder")

coded_with_norms$formatting = factor(coded_with_norms$formatting,
                                     levels = c("direct", "modal", "embedded modal", "indirect"))

ggplot(data=coded_with_norms, aes(x=judgment, fill=condition)) +
  geom_density(alpha=.4) +
  ggtitle("Appropriateness by formatting") +
  xlab("Appropriateness judgments (centered)") +
  theme_minimal() +
  facet_grid(~formatting)

ggsave("Figures/fig2_exp3.tiff", units="in", width=6, height=4, dpi=300, compression = 'lzw')

```



### Supplementary: Model comparisons for effect of power

```{r}

model_no_power_interaction = lmer(judgment ~ format_reordered + mean_power + 
                              format_reordered*mean_entitlement +
                              format_reordered*mean_distance +
                              format_reordered*mean_imposition +
                              Gender +
                             (1+mean_entitlement| subject) + (1 +mean_entitlement| stimNum) +
                             (1 | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

model_no_power = lmer(judgment ~ format_reordered*mean_entitlement +
                              format_reordered*mean_distance +
                              format_reordered*mean_imposition +
                              Gender +
                             (1+mean_entitlement| subject) + (1 +mean_entitlement| stimNum) +
                             (1 | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

anova(model_full_all_norms, model_no_power_interaction)
anova(model_no_power_interaction, model_no_power)

```

### Supplementary: Model comparisons for effect of imposition

```{r}

model_no_imposition_interaction = lmer(judgment ~ format_reordered*mean_power + 
                              format_reordered*mean_entitlement +
                              format_reordered*mean_distance +
                              format_reordered + mean_imposition +
                              Gender +
                             (1+mean_entitlement| subject) + (1 +mean_entitlement| stimNum) +
                             (1 | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

model_no_imposition = lmer(judgment ~ format_reordered*mean_entitlement +
                              format_reordered*mean_distance +
                              format_reordered*mean_power +
                              Gender +
                             (1+mean_entitlement| subject) + (1 +mean_entitlement| stimNum) +
                             (1 | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

anova(model_full_all_norms, model_no_imposition_interaction)
anova(model_no_imposition_interaction, model_no_imposition)

```

### Supplementary: Model comparisons for effect of distance

```{r}

model_no_distance_interaction = lmer(judgment ~ format_reordered*mean_power + 
                              format_reordered*mean_entitlement +
                              format_reordered*mean_imposition +
                              mean_distance +
                              Gender +
                             (1+mean_entitlement| subject) + (1 +mean_entitlement| stimNum) +
                             (1 | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

model_no_distance = lmer(judgment ~ format_reordered*mean_entitlement +
                              format_reordered*mean_imposition +
                              format_reordered*mean_power +
                              Gender +
                             (1+mean_entitlement| subject) + (1 +mean_entitlement| stimNum) +
                             (1 | group),
                           data = coded_with_norms,
                           control=lmerControl(optimizer="bobyqa"),
                           REML=FALSE)

anova(model_full_all_norms, model_no_distance_interaction)
anova(model_no_distance_interaction, model_no_distance)

```



#### Adjust for multiple comparisons

After adjusting for multiple comparisons, we see significant effects of: 

The interaction between *entitlement* and *formatting*.
The interaction between *social distance* and *formatting*.

```{r}
p1 = anova(model_full_all_norms, model_no_entitlement_interaction)$`Pr(>Chisq)`[2]
p2 = anova(model_no_entitlement_interaction, model_no_entitlement)$`Pr(>Chisq)`[2]
p3 = anova(model_full_all_norms, model_no_power_interaction)$`Pr(>Chisq)`[2]
p4 = anova(model_no_power_interaction, model_no_power)$`Pr(>Chisq)`[2]
p5 = anova(model_full_all_norms, model_no_imposition_interaction)$`Pr(>Chisq)`[2]
p6 = anova(model_no_imposition_interaction, model_no_imposition)$`Pr(>Chisq)`[2]
p7 = anova(model_full_all_norms, model_no_distance_interaction)$`Pr(>Chisq)`[2]
p8 = anova(model_no_distance_interaction, model_no_distance)$`Pr(>Chisq)`[2]

p.adjust(c(p1, p2, p3, p4, p5, p6, p7, p8), method="holm")
```

